SIMITAR: realistic and autoconfigurable traffic generation

### 2017-12-01 Docs/PaperSimitar/body.tex
up

Emerging technologies such as SDN and NFV are great promises. If succeeding at large-scale, they would change drastically the development and operation of computer networks. But, especially on NFV, its enabling technologies such as virtualization still pose challenges on performance,  reliability, and security\cite{nfv-challenges}. Closed hardware solutions are easier to pass on Service Layer Agreement since they have a much more predictable behavior. Since it is expected virtualization to impact negatively on performance, these VNFs have to keep its degradation as small as possible. Guarantee the Service Layer Agreements on emerging scenarios is now a harder question. There is a demand for more reliable methods to ensure the SLAs, over different types of loads.

It is already a well-known fact that the type of traffic used on performing tests matters. Studies show that a realistic Ethernet traffic provides a different and more variable load characteristics on routers\cite{harpoon-validation}, even with the same mean bandwidth consumption. It indicates that tests with constant bit rate traffic generator tools are not enough for a complete validation of new technologies. There are many reasons for this behavior, which includes burstiness and packet sizes.

A burstier traffic can cause packet more buffer overflows on network \cite{burstiness-queue-lenght} \cite{modelling-of-self-similar} \cite{empirical-interarrival-study}, degenerating network performance\footnote{Fuatures such as packet-trains periods and inter-packet times affect traffic burstiness}, and  measurement accuracy\cite{legotg-paper} \cite{background-traffic-matter}. Another key question is how applications will deal with packets. It is a well-known fact that applications have a huge performance degradation processing small packets\cite{comparative-trafficgen-tools}. A realistic synthetic traffic must not have a single packet-size but must use a distribution \cite{packet-distribution-model}.

Realistic workload generators are also essential security research\cite{ditg-paper}.  Generation of realistic workloads is important in the evaluation of firewall middleboxes. It includes studies of intrusion, anomaly detection, and malicious workloads\cite{ditg-paper}.

Since on traditional hardware-based types of \textit{middleboxes}, the impact of realistic traffic is not negligible; we can expect that its impact over virtualized middle-boxes should be even larger, due the extra overhead of a virtualization layer.

Another critical point is the flow-oriented operation of SDN networks. Each new flow arriving on an SDN switch demands an extra communication load between it and the controller. This may create a bottleneck between the switch and the controller.  Also the SDN switches have a flow-oriented operation. Since its operation relies on queries on flow tables, a stress load must have the same flow properties of an actual Internet Service Provider.

Therefore, there is a demand for the study of the impact of a realistic traffic on this new sort of environment. How VNFs and virtualized middle-boxes and SDN testbeds will behave if stressed with a realistic traffic load in comparison to a constant rate traffic is a relevant subject.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Open-source Solutions}\label{sec:review}

The open-source community offers a huge variety of workload generators and benchmarking tools \cite{ditg-paper}\cite{validate-trafficgen}\cite{comparative-trafficgen-tools}\cite{performance-trafficgen}. Most of these tools were built for specific purposes and goals, so each uses different methods of traffic generation, and enable controll of different features, such as throughput (bits/bytes per second, packets per seconds), packet-sizes, protocols and header customization, payload customization, inter-packet times, On/Off periodos, start and sending time, and emulation of applications such as Web server/client communication, VoIP, HTTP, FTP, p2p applications, and many more.

Some traffic generator tools offer support emulation of single application workloads. But this does not correspond to real complex scenarios. Other tools work as packet replay engines, such as TCPreplay and TCPivo. Although in that way is possible to produce a realistic workload at high rates, it comes with some issues. First, the storage space required becomes huge for long-term and high-speed traffic capture traces. Also, obtaining good traffic traces sometimes is hard, due privacy issues and fewer good sources.

Many tools support a larger set of protocols and high-performance, such Seagull and Ostinato. Others are also able to control inter-packet times and packet sizes using stochastic models, like D-ITG\cite{ditg-paper} and MoonGen. But all of them just offer a complet framework to be congfigured, but the customization of the traffic is all up to user to do. So, there is no simple way for the user to create an synthetic realistic traffic scenario.

We also have available a variety of APIs that enable creation of traffic and custom packets, wich include low-level APIs, such as Linux Socket API,  Libpcap, Libtins, DPDK, Pcapplusplus, libcrafter, impacket, scapy and many others. These APIs enable a finer controll and customization over each packet, and are used to implement traffic generators. For example, Ostinato and TCPreplay uses Libpcap, and MoonGen uses DPDK. Also, many of the listed traffic generators provides their own API, such as Ostinato Python API, D-ITG C API, and MoonGen LUA API.

>>>>

%> Burstiness de um trafego interfere nas medidas
It is already a well-known fact that the type of traffic used on tests impacts in many results, even with the same avarage bandwidth. Tests with constant bit rate traffic generator tools are not enough for a complete validation of new technologies. Realistic Ethernet traffic provides a different and more variable load characteristics on routers\cite{harpoon-validation}, even with the same avarage bandwidth. As reason we can for this behavior we have traffic burstiness and many different packet sizes\footnote{Traffic burstness is the intermitent increase and decreace on data transference. Fuatures such as packet-trains periods and inter-packet times affect traffic burstiness}.
A realistic burstier traffic can cause more buffer overflows, increase packet losses, cause a network performance degeneration \cite{burstiness-queue-lenght} \cite{modelling-of-self-similar} \cite{empirical-interarrival-study}, and interfere on the measurement acuracy \cite{legotg-paper} \cite{background-traffic-matter} compared to a constrant traffic. Also the traffic burstiness interferes on the  measurement accuracy.

%> Aplicações e middleboxes
Another key question is how applications will deal with packets. It is a well-known fact that applications have a huge performance degradation processing small packets\cite{comparative-trafficgen-tools}. A realistic synthetic traffic must not have a single packet-size but must use a distribution \cite{packet-distribution-model}.  Realistic workload generators are also essential security research\cite{ditg-paper}. It includes studies of intrusion, anomaly detection, and malicious workloads\cite{ditg-paper}, over firewall middleboxes and softwares. In this case, not just the traffic burstiness is relevant, but the connection behavior and header contents, such as protocols and port numbers.

%Emerging technologies such as SDN and NFV are  drastically changing  computer networks. But enabling technologies such as virtualization still pose challenges on performance,  reliability, and security\cite{nfv-challenges}. Closed hardware solutions are easier to pass on Service Layer Agreement since they have a much more predictable behavior. Guarantee the Service Layer Agreements on emerging scenarios is now a harder question. There is a demand for more reliable methods to ensure the SLAs, over different types of loads. Since on traditional hardware-based types of \textit{middleboxes}, the impact of realistic traffic is not negligible; we can expect an even larger impact over over virtualized middle-boxes should be even larger, due the virtualization layer extra overhead. Also, we have the flow-based ofperation of  SDN networks. Each new flow arriving on an SDN switch demands an extra communication load between it and the controller. This may create a bottleneck between the switch and the controller. The SDN switches have a flow-oriented operation, since it check each new packet in an flow-match table. Therefore an performance measurement must use a traffic with the same flow properties of an actual Internet Service Provider. Therefore, there is a demand for the study of the impact of a realistic traffic on this new sort of environment. How virtualized network functions,  virtualized middle-boxes and SDN switches and cotrollers will behave if stressed with a realistic traffic load in comparison to a constant rate traffic is an important study subject. 
Emerging technologies such as SDN and NFV are  drastically changing  computer networks. But enabling technologies such as virtualization still pose challenges on performance,  reliability, and security\cite{nfv-challenges}, since hardware solutions  have a much more predictable behavior. There is a demand for more reliable methods to ensure the Service Layer Agreements, over different types of loads. We can expect an even larger impact over over virtualized middle-boxes should be even larger compared to dedicated hardware devices, due the virtualization-layer extra overhead. Along with that, on Software Defined Networks we have the flow-based operation. Each new flow arriving on an SDN switch demands an extra communication between it and the controller, wich may create a boobleneck. The SDN switches have a flow-oriented operation, since it check each new packet in an flow-match table. Therefore an performance measurement must use a traffic with the same flow properties of an actual Internet Service Provider. Therefore, there is a demand for the study of the impact of a realistic traffic on this new sort of environment. How virtualized network functions,  virtualized middle-boxes and SDN switches and cotrollers will behave if stressed with a realistic traffic load in comparison to a constant rate traffic is an important study subject.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Open-source Traffic Generators}\label{sec:review}

The open-source community offers a huge variety of workload generators and benchmarking tools \cite{ditg-paper}\cite{validate-trafficgen}\cite{comparative-trafficgen-tools}\cite{performance-trafficgen}. Most of these tools were built for specific purposes and goals, so each uses different methods of traffic generation, and enable controll of different features, such as throughput (bits/bytes per second, packets per seconds), packet-sizes, protocols and header customization, payload customization, inter-packet times, On/Off periodos, start and sending time, and emulation of applications such as Web server/client communication, VoIP, HTTP, FTP, p2p applications, and many more. Traffic generators are commonly classified into four different groups\cite{do-you-trust}: application-level, flow-level, packet-level and multi-level traffic generators.

\textbf{Application-level traffic generators}: they try to emulate the behavior of network applications, simulating real workloads stochastically and/or responsively \footnote{Responsiveness refers to the property of capacity of response over time of the workload tool. That means, the behavior of the output may change according to what packets have arrived in the network interface}. As examples we have Surge\cite{surge-paper} able to emulate the behavior of web clients and services. The behavior of such applications is, in general, based on request-response exchanges models.

\textbf{Flow-level traffic generators}: they are able to configure and reproduce features of flows\cite{do-you-trust}\cite{sourcesonoff-paper}, such as flow duration, start times distributions, and temporal (diurnal) traffic volumes\cite{do-you-trust}. Harpoon \cite{harpoon-paper} is able to extract these parameters from Cisco NetFlow data, collected from live routers.

\textbf{Packet-level traffic generators}: most traffic generators available fall in this class. They are able to craft packets and inject into the network, and controll features like inter departure times (IDT), packet size(PS), throughput and packets per second\cite{validate-trafficgen}. \cite{validate-trafficgen} classify them as replay engines, maximum throughput generators, and model based generators. Traffic Replay engines, such TCPreplay\cite{web-tcpreplay}, are  able to read packet capture files (\textit{pcap} files), and inject copies on a network interface. Model-based generators, such D-ITG \cite{ditg-paper}, TG\cite{web-tg}, may have PS and IDT configured by the user. They can configure IDT  either by constant values (defining the packet rate or bandwidth) or by stochastic models. Maximum throughput engines like Ostinato and Seagull are tools that the main goal is to perform end-to-end stress testing. Are included in this category generators that are able to craft packets from the link layer, like Brute, KUTE, and pktgen.

\textbf{Multi-level traffic generators}: its proposal is to take into account existing interaction among each layer of the network stack, to create background network traffic as close as possible from reality. The most relevant tool of this class is Swing \cite{swing-paper}. Swing take into account many points of each layer, using an approach based on randomness and responsiveness \cite{swing-paper}. That means, it uses packet-sizes and inter packet times stochastic models, but also take into account flow and application layer behavior. Swing is able to model things like\cite{swing-paper}:

\begin{itemize}

	\item User behavior: Number of request and responses, time between requests and responses;

	\item Request and Responses: number of connections, time between start of connections;

	\item Connection: Number of request and responses per connection, applications modeling (HTTP, P2P, SMTP), transport protocols TCP/UDP based on the application, response sizes, request sizes, user think between exchanges on a connection;

	\item Packet: packet size (Maximum transmission unit), IP addresses, (MTU), bit rate and packet arrival distribution,

	\item Link: link Latency Delay, loss rates.

\end{itemize}

Swing take as input collected \textit{pcap} files. Botta at al. \cite{do-you-trust} argues that due its complexity, they are rarely used to conduct experimental researchers. Also, we can  justify due its overheads, since the performance of such complex traffic generator is limited\cite{legotg-paper}. The authors Vishwanat et al. \cite{swing-paper} cite that they have generated traces of about of 200 Mbps, about the same result found by \cite{legotg-paper}. In the other hand, D-ITG reached 9808 Mbps\cite{comparative-trafficgen-tools} in a link of 10 Gbps, but operating as a maximum throughput generator.

Application level traffic generators may be realistic from a server operation system perspective, but are not able to represent real complex scenarios. Replay engines such as  TCPreplay and TCPivo have some limitation. First, they usually do not replicate the same inter-packet times form the original trace, just creates a constant bandwidth traffic. They also requere storage of \textit{pcap} files, wich may become huge for  long-term and high-speed traffic capture traces. Also, obtaining good traffic traces sometimes is hard, due privacy issues and limited sources.  Many tools support a larger set of protocols and high-performance, such Seagull and Ostinato. Others are also able to control inter-packet times and packet sizes using stochastic models, like D-ITG\cite{ditg-paper} and MoonGen. But all of them just offer a complet framework to be congfigured, but the customization of the traffic is all up to user to do. So, there is no simple way for the user to create an synthetic realistic traffic scenario.

We also have available a variety of APIs that enable creation of traffic and custom packets, wich include low-level APIs, such as Linux Socket API,  Libpcap, Libtins, DPDK, Pcapplusplus, libcrafter, impacket, scapy and many others. These APIs enable a finer controll and customization over each packet, and are used to implement traffic generators. For example, Ostinato and TCPreplay uses Libpcap, and MoonGen uses DPDK. Many of the listed traffic generators provides their own high-level API, such as Ostinato Python API, D-ITG C API, and MoonGen LUA API.

### 2017-12-01 Docs/PaperSimitar/header.tex
up

\begin{abstract}
It is a well known fact that the type of traffic on network measurements matters. A realistic Ethernet have a different impact compared to constant traffic tools like Iperf, even with the same bandwidth. A burstier traffic may cause buffers overflows when a constant traffic does not, decrease on the measurement acuracy. The number of flows of a traffic may have an impact of flow-oriented nodes, such as SDN switches and controllers. Today in an scenario where software defined networks are going to play an essential role in the future of the networks, a depper validation of new technologies in order to guarantee the SLAs is crucial. In this scenario we come with an anternative for realist traffic generation. Most of open-source realistic traffic generator tools have the modelling layer coupled to the traffic generator API, wich make it difficult to be update to newer lybraries, or require user programming and manual configuration. We propose a sollution called SIMITAR: SnIffing, ModellIng and TrAffic geneRation, that have a separated moddelling framework from the traffic generator, which is flow-oriented, and is autoconfigurable. It creates and use as imputs compact traces descriptos, XML files that describes all features of the traffics. 
Currently we are able to replicate with acuracy 
\end{abstract}

>>>>

\begin{abstract}
It is a well known fact that the type of traffic on network measurements matters. A realistic Ethernet traffic have a different impact over a device compared to constant traffic (such as generated by Iperf), even with the same avarage bandwidth. A burstier traffic can cause more buffers overflows, increace losses and decrease on the measurement acuracy. The number of flows of a traffic may have an impact of flow-oriented nodes, such as SDN switches and controllers. Therefore, in an scenario where software defined networks are going to play an essential role in the future of the networks, a depper validation of new technologies in order to guarantee the SLAs is crucial. In this scenario we come with an anternative for realist traffic generation. Most of open-source realistic traffic generator tools have the modelling layer coupled to the traffic generator API, wich make it difficult to be update to newer lybraries, or require user programming and manual configuration. We propose a sollution called SIMITAR: SnIffing, ModellIng and TrAffic geneRation, wich separetes the processes of data collection, modelling and traffic generation, is flow-oriented, and is autoconfigurable. It creates and use as imputs compact traces descriptos, XML files that model a network trace. Currently we are able to replicate with acuracy some applications traffics and the flow-level properties from the traffic.
\end{abstract}
